---
title: "Designing Choice Experiments using the support.CEs package."
author: Sidney Sherborne^[The Cognition Company, sidney.sherborne@cognitioncompany.com]
output:
  pdf_document:
    toc: false
  header-includes:
    - \usepackage{hyperref}
---

This is a quick guide to using the [support.CEs]() package to design a choice experiment. This is currently limited to forced-choice experiments with binary attributes (i.e.\ the attribute is present or not present).

The following packages are used in the following code. Install these first.

```{r, echo = TRUE, message = FALSE}
# These packages are required for the code to work. 
# Remove the # symbol to uncomment them so they will run.

# install.packages("support.CEs")
# install.packages("dplyr")
# install.packages("kableExtra")

library(support.CEs)
library(dplyr)
library(kableExtra)
```

Below is a custom function which takes an input number of binary attributes and returns the design matrix.

```{r, echo = TRUE, message = FALSE}
create_design <- function(n_attributes) {
  
  # Creating the list of 4 attributes with two levels each.
  attribute_list <<- list(paste0("A", 1:2))
  
  for (i in 2:n_attributes){
    attribute_list[i] <<- list(c(paste0(LETTERS[i],1), 
                              paste0(LETTERS[i],2)))
  }
  
  # Plugging list into the support.CEs function.
  design_4 <- Lma.design(attribute.names = attribute_list, 
                         nalternatives =  2, 
                         nblocks = 1)
  
  # Getting design matrix.
  design_matrix <- make.design.matrix(design_4, 
                                      categorical.attributes = paste0("X",1:n_attributes), 
                                      binary = FALSE)
  
  # Removing the 'no choice option'.
  design_matrix <- design_matrix %>% filter(!ALT == 3) %>%
  # Recoding 1 and 0 to Yes and No.
    mutate_at(.vars = paste0(LETTERS[1:n_attributes],2),
              function(x) ifelse(x==1, "Yes", "No"))  %>% 
    select(QES, paste0(LETTERS[1:n_attributes],2))
  
  # Renaming Table Names
  names(design_matrix) <- c("Question", paste0("Attribute ", 1:n_attributes))
  
  return(design_matrix)
}

```

The code below selects the number of attributes. Then displays the table containing the structure of the choice experiment. The result of the table can be found in Table \ref{tab:structure}.

```{r, echo = TRUE, message=FALSE, warning=FALSE, results='asis'}
# Select number of attributes.
n_attributes <- 4

# Run the function above.
create_design(n_attributes) %>% 
# Format the resulting table.
  kable(caption = "Structure of experiment.", 
        label = "structure", 
        booktabs = T, 
        align = "c", 
        escape = F, 
        linesep = c('','\\addlinespace\\hline\\addlinespace')) %>% 
  kable_styling("condensed", 
                full_width = F, 
                latex_options=c("scale_down","HOLD_position")) %>% 
  print()
```